Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-13 article.tex
Fixes according to Yoav

\begin{abstract}
  Aerosols affect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer. We propose a principle to estimate the
  aerosol distribution as it really is: a three dimensional (3D)
  volume.  The principle is a type of
  tomography. The process involves wide angle integral imaging of the
  sky on a very large scale. The sensing can use an array of cameras in visible light.
  We formulate an image formation model
  based on 3D radiative transfer. Model inversion is done using optimization methods,
  exploiting a closed-form gradient which we derive for the model-fit
  cost function.  The tomography model is distinct, as the radiation
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.
\end{abstract}

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
To demonstrate the model, we simulated some scenarios, whose details are as follows.
\\

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. For clarity of display, the brightness of the
displayed pictures in this paper underwent the same standard
contrast enhancement (stretching), including gamma-correction.
The recovery algorithms, of course, have used the raw (not brightness
enhanced) images.

@@

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
estimation~\cite{marshak20053d} derives the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) compares photographs of the {\em Haze Blobs} scene described in \cref{sec:simul}.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see \cref{sec:optimization-results}).
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
    The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
  }
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributions
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC
(See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function. (d) High aerosol density.}
  \label{fig:simulation_particles}
\end{figure}
Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
and \ref{fig:reconstructions}(b)
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
    has isotropic phase function (b) or has high density (c).}
  \label{fig:reconstructions}
\end{figure}
and in \cref{tbl:mass}. The results indicate that if the aerosol's phase function
has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesize that
tomography is better served by scattering isotropy, since then significant radiance from
any voxel reaches cameras in a wide range of directions. This may make back-projection
(recovery from cameras to voxels) more accurate. On the other hand, if the phase function
is too strongly peaked around one direction, most cameras would not receive much scattered
radiance from a voxel, undermining tomography. A very broad research is needed to verify
and quantify such dependencies.\\

@@

We are grateful to David~J. Diner for fruitful discussions and his support at all
levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
Fellow - supported by the Taub Foundation. This work is supported by the
US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
Ollendorff Minerva Center. Minerva is funded through the BMBF. This work was supported
by NASA's Earth Science Technology Office Advanced Information Systems Technology Program.

>>>>

\begin{abstract}
  Aerosols affect climate, health and aviation.  Currently, their
  retrieval assumes a plane-parallel atmosphere and solely vertical
  radiative transfer. We propose a principle to estimate the
  aerosol distribution as it really is: a three dimensional (3D)
  volume.  The principle is a type of
  tomography. The process involves wide angle integral imaging of the
  sky on a very large scale. The imaging can use an array of cameras in visible light.
  We formulate an image formation model
  based on 3D radiative transfer. Model inversion is done using optimization methods,
  exploiting a closed-form gradient which we derive for the model-fit
  cost function.  The tomography model is distinct, as the radiation
  source is unidirectional and uncontrolled, while off-axis scattering
  dominates the images.
\end{abstract}

@@

\begin{figure}
  \centering
  \yoavcomment{\includegraphics[width=\linewidth]{images/single_images.pdf}}
  \caption{\small Different viewpoints of a sky that includes {\em
      Haze Blobs}. Images are rendered using the single-scattering model.
    A yellow dot marks the Sun location. Dashed white circles mark
    zenith angles.}
  \label{fig:simulation-results1}
\end{figure}
\Cref{fig:simulation-results1} shows examples of photographs rendered
using the single-scattering model. To create these photographs we
simulated several scenarios, whose details are as follows.
\\

@@

\noindent{\bf Aerosol}: We used particle-type 6 from the aerosol list
in~\cite{Martonchik2009}. This is a spherical non-absorbing
sea-salt/organic particle, whose anisotropy parameter per color
channel is $[g_{\rm R},g_{\rm G},g_{\rm B}]=[0.763,0.775,0.786]$. Its
corresponding extinction cross sections are $[\sigma^{\rm
  aerosol}_{\rm R}, \sigma^{\rm aerosol}_{\rm G}, \sigma^{\rm
  aerosol}_{\rm
  B}]=[16.5,16.2,15.9]$~\si[sticky-per]{\per\micro\meter\squared}.  At
all channels, $\varpi^{\rm aerosol}=1$. We simulated spatial
distributions using a product of two functions. To express the general
trend of reduced density with altitude $h(k)$ of voxel $k$, we
follow~\cite{Levi1980} and set the first function as
\begin{align}
  f_1[h(k)] = n^{\rm sealevel}
  \exp[-h(k)/H^\mathrm{aerosol}],
\end{align}
where $H^\mathrm{aerosol}=2$~\si{\km}. To express a clustered nature
of aerosol distributions (as clouds), we define blobs in the form of
3D ellipsoids. There may be multiple ellipsoids suspended.  Then
\begin{equation}
  f_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then ${\bm n}^{\rm true}={\cal
  S}\{{\bm f}_1\odot {\bm f}_2\}$, where ${\cal S}$ is 3D spatial
smoothing, obtained by narrow 3D Gaussian filtering. It expresses
non-sharp boundaries of typical distributions. The {\em Haze Blobs}
scene in \cref{fig:distributions}(a) uses two ellipsoids: one is 32km
wide, 2.8km thick and centered at altitude 2.5km; the other is 24km
wide, 2.1km thick and centered at altitude 5km. Horizontal widths
are much larger than the vertical thickness, in consistency with
atmospheric scales. \Cref{fig:simulation-results1} shows
photographs of the {\em Haze Blobs} scene, as simulated by
\cref{eq:bigIA}. For clarity of display, the brightness of the
displayed pictures in this paper underwent the same standard
contrast enhancement (stretching), including gamma-correction.
The recovery algorithms, of course, uses the raw (not brightness
enhanced) images.

@@

\noindent ({\tt v}) The photon-packet is scattered to a new direction,
determined by inverse transform sampling, according to the phase
function of the particle (Eqs.~\ref{eq:aerosol_scatter}
or~\ref{eq:rayleighP}). This yields a new {\em ray}, denoted ${\cal
  R}_{i+1}$, emanating from ${\bf X}_{i}$. Local
estimation~\cite{marshak20053d} derives the amount of
light back-traced to the sun at each scattering. The next iteration of
propagation (denoted {\tt ii} above) proceeds.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
    The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
  }
  \label{fig:cross_sections}
\end{figure}
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small Images simulated by MC, from the same viewpoint, but different
  aerosol characteristics. (a) Haze blobs, characterized in Sec.~\ref{sec:simul}. 
  (b) Partly absorbing aerosol. (c) Aerosol having an isotropic phase function.
  (d) High aerosol density. Details of the scenarios used in creating (b) and
  (c) are given in \cref{sec:optimization-results}.}
  \label{fig:simulation_particles}
\end{figure}

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.
\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributions
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

@@

\noindent{\bf Aerosol characteristics}: We used the {\em Haze blobs} scene, but varied the
aerosol characteristics. Compared to the aerosol described in \cref{sec:simul}, we tested two variations. In one variation, the phase function was isotropic, i.e.,
$[g_{\rm R},g_{\rm G},g_{\rm B}]=[0,0,0]$. In the other variation, the aerosol is partly absorbing: its single scattering albedo per color channel is
$[\varpi^{\rm aerosol}_{\rm R},\varpi^{\rm aerosol}_{\rm G},\varpi^{\rm aerosol}_{\rm B}]=
[0.69,0.74,0.78]$.  All rendered images used MC
(See Figs.~\ref{fig:simulation_particles}(a)--\ref{fig:simulation_particles}(c)).
Recovery results using $N_{\rm views}=36$ are shown in Figs.~\ref{fig:reconstructions}(a)
and \ref{fig:reconstructions}(b)
\begin{figure}[b]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small  Recovered distributions when the aerosol is either party absorbing (a),
    has isotropic phase function (b) or has high density (c).}
  \label{fig:reconstructions}
\end{figure}
and in \cref{tbl:mass}. The results indicate that if the aerosol's phase function
has smaller anisotropy, recovery of the aerosol's density is easier. We hypothesize that
tomography is better served by scattering isotropy, since then significant radiance from
any voxel reaches cameras in a wide range of directions. This may make back-projection
(recovery from cameras to voxels) more accurate. On the other hand, if the phase function
is too strongly peaked around one direction, most cameras would not receive much scattered
radiance from a voxel, undermining tomography. A very broad research is needed to verify
and quantify such dependencies.\\

@@

We are grateful to David~J. Diner for fruitful discussions and his support at all
levels. We thank the reviewers for useful comments. Yoav Schechner is a Landau
Fellow - supported by the Taub Foundation. This work is supported by the
US-Israel Binational Science Foundation (BSF grant 2012202) and conducted in the
Ollendorff Minerva Center. Minerva is funded through the BMBF. Part of this work
was performed at the Jet Propulsion Laboratory, California Institute of Technology,
under contract with NASA and with support by NASA's Earth Science Technology Office
Advanced Information Systems Technology Program.
